DisCon Speaker Change Adult Analysis

### 2018-12-21 analysis/01_adult_speakerchange.Rmd
change introduction of speaker change experiment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) #no code, no warning printed
library(knitr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
library(ggthemes)
library(langcog)
```

#Pilot 1 data
```{r data preprocessing}
# Data pre-processing

files <- dir("../../adult_600_speakerchange/sandbox-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_speakerchange/sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```

```{r}
data_ip <- data %>%
  filter(phase == 'training') %>%
  group_by(workerIp) %>%
  summarise(correct = mean(correct_item))
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)
```
```{r}

sample_size <- data %>%
  distinct(workerid, .keep_all = TRUE)

sample_size %>%
 group_by(experiment) %>%
 summarise(n = n())
```

```{r plot1}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, speakerChange) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -speakerChange) %>%
  group_by(distribution, item, speakerChange) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~speakerChange, 
             labeller = as_labeller(c(change = "speaker change", same = "no change"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")

```
